The Effect of Media Frames on Issue Attitudes

### 2021-10-04 paper/main.tex

Again, most estimates are not significant, differ in direction across specifications, and cluster around 0. While some estimates are unidirectional (crime and labour market in the immigration issue), they show tiny effects (a standard deviation increase in attention to the labour market ) and

>>>>

Again, most estimates are not significant, differ in direction across specifications, and cluster around 0. While some estimates are unidirectional (crime and labour market in the immigration issue), they show tiny effects (a standard deviation increase in attention to the labour market makes issue attitudes 0.015 standard deviations more conservative) and are usually not significant. Most importantly, both models do not correspond to expectations. This is probably most visible for the capital and sex crime frame ('capcrime'), which should show strongly positive effects (leading to more restrictive attitudes), but also for the illegal immigration and petty crime frame ('crime'), which shows consistently negative (i.e. liberalising) effects.
